MINOS Handover Plots

### 2023-07-13 minos/validation/handovers.Rmd
Added active var to handovers and cross-validation

```{r}
prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'education_state')

var <- prepped.list$var
norm <- prepped.list$norm

tit <- 'Education State'

# Now plot
ggplot(data = var, mapping = aes(x = time, y = n, group = education_state, colour = education_state)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = tit, subtitle = 'Counts by Level') +
  xlab('Year') +
  ylab('Count')

ggplot(data = norm, mapping = aes(x = time, y = prct, fill=education_state)) +
  geom_bar(stat = 'identity') +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = tit) +
  xlab('Year') +
  ylab('Proportion')

if (shall.we.save) {
  ggsave(filename = 'education_state.png',
         plot = last_plot(),
         path = save.path)
}

rm(prepped.list, var, norm, tit)
```

@@

```{r}

```

>>>>

```{r}
handover_ordinal(raw.dat, base.dat, var = 'education_state', save = shall.we.save)
```

@@

## Alcohol (AUDITC)

```{r}
handover_ordinal(raw.dat, base.dat, var = 'auditc', save = shall.we.save)
```

## Physical Activity

```{r}
handover_ordinal(raw.dat, base.dat, var = 'active', save = shall.we.save)
```
